We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-04-17 paper/paper.tex
updated table
tabla actualizada

\begin{table*}
  \centering
  \renewcommand{\arraystretch}{1.2}
  \begin{tabular}{|p{2.5cm}|c|c|c|c|c|c|}
    \hline
    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Observations}}
    & \multicolumn{2}{c|}{\textbf{Randomized Obs.}} &
    \multicolumn{2}{c|}{\textbf{Normalized Units}}\\
    % \hline
    % \textbf{Inactive Modes} & \textbf{Description}\\
    \cline{2-7}
    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} \\
    %\hhline{~--}
    \hline
Plane width (kpc) & $63.64$ & $19.34$ & $55.78$ & $38.60$ & $0.74$ & $-4.45$\\\hline
$c/a$ ratio & $0.42$ & $0.18$ & $0.51$ & $0.45$ & $-0.87$ & $-2.75$\\\hline
$b/a$ ratio & $0.96$ & $0.87$ & $0.82$ & $0.83$ & $1.74$ & $0.67$\\\hline
  \end{tabular}
  \caption{Results from observations with $N_s=11$. 
    for the different
    quantities describing the satellite distributions: plane width, $c/a$
    ratio and $b/a$ ratio. 
    The first column refers to the results from
    observational data, the second column uses the spherically
    randomized version of the observational data, the third column
    corresponds to the observational data recentered and normalized
    by the standard deviation of the randomized data. \label{table:observations}}
\end{table*}

\begin{table*}
  \centering
  \renewcommand{\arraystretch}{1.2}
  \begin{tabular}{|p{2.5cm}|c|c|c|c|c|c|}
    \hline
    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Illustris-1-Dark}} & \multicolumn{2}{c|}{\textbf{Illustris-1}} & \multicolumn{2}{c|}{\textbf{ELVIS}}\\
    % \hline
    % \textbf{Inactive Modes} & \textbf{Description}\\
    \cline{2-7}
    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW}& \textbf{M31} & \textbf{MW}\\
    %\hhline{~--}
    \hline
    Plane width (kpc) & $62\pm 3$   & $61\pm 3$     & $70\pm 4$ & $67\pm 2$ & $70\pm 2$& $68\pm 4$ \\\hline
    $c/a$ ratio & $0.50\pm0.01$ & $0.50\pm 0.02$ & $0.52\pm 0.01$ & $0.53\pm 0.01$ & $0.54\pm 0.01$& $0.49\pm 0.02$ \\ \hline
    $b/a$ ratio & $0.79\pm0.01$ & $0.81\pm 0.02$ & $0.80\pm 0.01$ & $0.80\pm 0.02$ & $0.80\pm0.01$& $0.81\pm 0.01$\\ \hline
  \end{tabular}
  \caption{Results from simulations. Mean values and standard deviations for the different
    quantities describing the satellite distributions: plane width, $c/a$
    ratio and $b/a$ ratio. 
    The first column summarizes the results from the 24 pairs in
    Illustris-1-Dark, the second column from the 20 pairs in
    Illustris-1 and the third column from the 12 pairs in the
    ELVIS project.\label{table:simulations}}
\end{table*}

>>>>

\begin{table*}
  \centering
  \renewcommand{\arraystretch}{1.2}
  \begin{tabular}{|p{2.5cm}|c|c|c|c|c|c|}
    \hline
    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Observations}}
    & \multicolumn{2}{c|}{\textbf{Randomized Obs.}} &
    \multicolumn{2}{c|}{\textbf{Normalized Units}}\\
    % \hline
    % \textbf{Inactive Modes} & \textbf{Description}\\
    \cline{2-7}
    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} \\
    %\hhline{~--}
    \hline
Plane width (kpc) & $63.64$ & $19.34$ & $55.78\pm10.65$ & $38.60\pm8.19$ & $0.74$ & $-4.45$\\\hline
$c/a$ ratio & $0.42$ & $0.18$ & $0.51\pm0.11$ & $0.45\pm0.12$ & $-0.87$ & $-2.75$\\\hline
$b/a$ ratio & $0.96$ & $0.87$ & $0.82\pm0.08$ & $0.83\pm0.08$ & $1.74$ & $0.67$\\\hline
  \end{tabular}
  \caption{Results from observations with $N_s=11$. 
    for the different
    quantities describing the satellite distributions: plane width, $c/a$
    ratio and $b/a$ ratio. 
    The first column refers to the results from
    observational data, the second column uses the spherically
    randomized version of the observational data, the third column
    corresponds to the observational data recentered and normalized
    by the standard deviation of the randomized data. \label{table:observations}}
\end{table*}

\begin{table*}
  \centering
  \renewcommand{\arraystretch}{1.2}
  \begin{tabular}{|p{2.5cm}|c|c|c|c|c|c|}
    \hline
    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Illustris-1-Dark}} & \multicolumn{2}{c|}{\textbf{Illustris-1}} & \multicolumn{2}{c|}{\textbf{ELVIS}}\\
    % \hline
    % \textbf{Inactive Modes} & \textbf{Description}\\
    \cline{2-7}
    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW}& \textbf{M31} & \textbf{MW}\\
    %\hhline{~--}
    \hline
Plane width (kpc) & $56.28\pm 18.30$ & $58.30 \pm 13.51$  & $66.66\pm 15.75$ & $64.81\pm 15.34$ & $68.74\pm 16.82$ & $63.70\pm 13.62$\\\hline
$c/a$ ratio & $0.48\pm 0.15$ & $0.47 \pm 0.11$  & $0.52\pm 0.13$ & $0.50\pm 0.10$ & $0.54\pm 0.15$ & $0.47\pm 0.13$\\\hline
$b/a$ ratio & $0.80\pm 0.10$ & $0.80 \pm 0.08$  & $0.82\pm 0.09$ & $0.82\pm 0.07$ & $0.81\pm 0.07$ & $0.80\pm 0.09$\\\hline
  \end{tabular}
  \caption{Results from simulations for $N_s=11$. Mean values and standard deviations for the different
    quantities describing the satellite distributions: plane width, $c/a$
    ratio and $b/a$ ratio. 
    The first column summarizes the results from the 27 pairs in
    Illustris-1-Dark, the second column from the 23 pairs in
    Illustris-1 and the third column from the 12 pairs in the
    ELVIS project.\label{table:simulations}}
\end{table*}
